---
title: "read and plot SBE CTD cnv-files"
author: "Marko Lipka, David Kaiser"
date: "`r lubridate::today()`"
output: github_document
---

`read.cnv.file()` function takes a filename of a .cnv file as argument and returns a data.frame.

`plot.CTD.data()` function 

- takes the output of `read.cnv.file()` and returns a facetted ggplot.
- optional arguments:
    + depvar: character (vector) of parameter(s) that should be used as depth axis. First match in parameter names will be used if multiple parameters are defined.
    + not2plot: character (vector) of parameter(s) that should not be plotted. default is a list of common metadata parameters like "*scan*", "*nbin*", "*flag*", "*latitude*", ...



```{r setup, include=FALSE}
library(knitr)
library(pander)
knitr::opts_chunk$set(echo = TRUE, fig.width=15, fig.height=4)
source("read.cnv.files.R")
source("plot.CTD.data.R")
```

# Examples

## V0001F01.cnv

```{r Example1}
Ex1 <- read.cnv.file("example data/V0001F01.cnv")

knitr::kable(head(Ex1$data))
pander(Ex1$meta)

plot.CTD.data(Ex1)
```

## P0009F01.cnv

```{r Example2}
Ex2 <- read.cnv.file("example data/P0009F01.cnv")

knitr::kable(head(Ex2$data))
pander(Ex2$meta)

plot.CTD.data(Ex2)
plot.CTD.data(Ex2, depvar = "prDM")
plot.CTD.data(Ex2, depvar = "sigma.é00", not2plot = c("flag", "nbin", "nbf", "upoly0", "upoly1"))
plot.CTD.data(Ex2, not2plot = "par")
```


```{r pressure, echo=FALSE, fig.width=12, fig.height=4, eval = F}
library("reshape2")
melted.df.1 <- melt(Ex1$data,
                  id.vars = c("depSM", "scan", "nbin",
                              "flag", "timeS", "nbf",
                              "altM", "prDM",
                              "header.latitude", "header.longitude"
                              ))

melted.df.2 <- melt(Ex2$data,
                  id.vars = c("depSM", "scan", "nbin",
                              "flag", "timeS", "nbf",
                              "altM", "prDM", "spar",
                              "header.latitude", "header.longitude",
                              "latitude", "longitude"
                              ))

library("ggplot2")
ggplot(melted.df.1,
       aes(x = depSM, y = value)) +
    geom_line() +
    scale_x_reverse() +
    coord_flip() +
    facet_grid(.~variable, scales = "free") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(melted.df.2,
       aes(x = depSM, y = value)) +
    geom_line() +
    scale_x_reverse() +
    coord_flip() +
    facet_grid(.~variable, scales = "free") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
